Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-10-20 documentation/paper.tex
Added back image grid search that was actually done with wall cuts

It became evident very quickly that a high resolution was not required to get a high accuracy relative to the ground truth data. $FourierMLP(\beta_{8})$ managed an excellent 98\% validation accuracy, and also produced a mean class-wise standard deviation of 0.29. Its very decisive prediction distribution can be observed in Figure \ref{banded_no_pos_input_hist}. Increasing the number of bands to $FourierMLPWithPos(beta_{20}, \chi)$, did not improve the results; accuracy only reached 95\%, with an increased mean standard deviation of 0.42. Using 40 bands reduced the accuracy once again, to 91\%.

@@

Throughout a variety of different network architectures, the best validation accuracy obtained was a deceptively high 85\%. The corresponding training accuracy of 100\% indicates that severe overfitting is taking place (not unexpected, given the relatively small image data set). Also, the class-wise standard deviation was a very high 0.95, which implies its decisions are nearly random (as seen in Figure \ref{image_hist}). It is likely fitting on some form of noise within $\iota$. The fact that throughout many trials (including a grid search), no good performance on validation data was observed, provides significant evidence that images provide insufficient information for effective discrimination.

\begin{figure}[h]
    \centering
    % includegraphics[width=\textwidth]{image_hist}
    \caption{\label{image_hist} Prediction distribution of the best $ImageConv(\iota)$ discriminator.}
\end{figure}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Performance of $ImageConv(\iota)$ configurations.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Convolutional Layers & Dense Layers & Max Accuracy & Precision & Recall & CWSD \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

The high standard deviations across the board are further evidence for the hypothesis that there is insufficient information in the image data.

The 100\% recall statistics are not due to high classification accuracy, but rather due to the network making predictions less than 0.5 for all examples of both classes.

>>>>

It became evident very quickly that a high resolution was not required to get a high accuracy relative to the ground truth data. $FourierMLP(\beta_{8})$ managed an excellent 98\% validation accuracy, and also produced a mean class-wise standard deviation of 0.29. Its very decisive prediction distribution can be observed in Figure \ref{banded_no_pos_input_hist}. Increasing the number of bands to 20 did not improve the results; accuracy only reached 95\%, with an increased mean standard deviation of 0.42. Using 40 bands reduced the accuracy once again, to 91\%.

@@

Throughout a variety of different network architectures, the best validation accuracy obtained was 69\%. The corresponding training accuracy of 100\% indicates that severe overfitting is taking place (not unexpected, given the relatively small image data set). Also, the class-wise standard deviation was a very high 0.99, which implies its decisions are nearly random (as seen in Figure \ref{image_hist}). It is likely fitting poorly on some form of noise within $\iota$. The fact that throughout many trials during a grid search, no good performance on validation data was observed, provides significant evidence that images provide insufficient information for effective discrimination.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{image_hist}
    \caption{\label{image_hist} Prediction distribution of one of the best $ImageConv(\iota)$ discriminators.}
\end{figure}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Performance of $ImageConv(\iota)$ configurations, trained without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Convolutional Layers & Dense Layers & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            0 & 0 & 6 & 3 & 69\% & 69\% & 100\% & 0.99 \\
            % ../experimental_data/validation_results/2018_07_29_image_grid_search/image_grid_search_l2_lambda0_dropout0_convolutional_layers_per_group2time1532891695_epoch15.json 
            \hline
            0.01 & 0.25 & 6 & 3 & 68\% & 68\% & 100\% & 0.98 \\
            % ../experimental_data/validation_results/2018_07_29_image_grid_search/image_grid_search_l2_lambda0.01_dropout0.25_convolutional_layers_per_group2time1532895825_epoch2.json
            \hline
            0.003 & 0.25 & 9 & 3 & 68\% & 68\% & 100\% & 0.98 \\
            % ../experimental_data/validation_results/2018_07_29_image_grid_search/image_grid_search_l2_lambda0.003_dropout0.25_convolutional_layers_per_group3time1532895118_epoch3.json
            \hline
            0.01 & 0.25 & 12 & 3 & 68\% & 68\% & 100\% & 0.97 \\
            % ../experimental_data/validation_results/2018_07_29_image_grid_search/image_grid_search_l2_lambda0.01_dropout0.25_convolutional_layers_per_group4time1532896126_epoch0.json
            \hline
            0.01 & 0.5 & 12 & 3 & 68\% & 68\% & 100\% & 0.99 \\
            % ../experimental_data/validation_results/2018_07_29_image_grid_search/image_grid_search_l2_lambda0.01_dropout0.5_convolutional_layers_per_group4time1532898944_epoch1.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

The high standard deviations across the board are further evidence for the hypothesis that there is insufficient information in the image data. The 100\% recall statistics are not due to high classification accuracy, but rather due to the network making predictions less than 0.5 for all examples of both classes.
